Lifting CDCL to Relational Domains

### 2016-10-15 domains.tex
sync, some stuff on transformers

\begin{definition}
 A \emph{meet decomposition} of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$a=\bigsqcap_{m\in M} m$.
%$forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Transformers}
%
In a typical abstract interpretation based Galois-connection setting
over an over-approximate domain, every concrete element has a unique
over-approximate representation in the abstract.  Likewise, every
concrete transformer is over-approximated by a unique abstract
transformer.  We now define an abstract deduction transformer.

@@

% For a program with $N$ variables, let $L$ be the total number of 
% meet irreducibles returned by a domain $D$.  For $D$ = {\em ItvDom}, the 
% maximum value of $L$ is $2*N$, whereas the maximum value of $L$ is 
% $2*(N^2)$ for $D$ = {\em OctDom}. Note that an octagon is the conjunction 
% of all octagonal inequalities in the set $L$.
%
%========================
\input{literals-clauses}
%========================

>>>>

\begin{definition}
 A \emph{meet decomposition} $\mathit{decomp}(a)$ of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$a=\bigsqcap_{m\in M} m$.
%$forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Transformers}
%-------------------------------------------------------------------------------
In a typical abstract interpretation based Galois-connection setting
over an over-approximate domain, every concrete element has a unique
over-approximate representation in the abstract.  Likewise, every
concrete transformer is over-approximated by a unique abstract
transformer.  We now define an abstract deduction transformer.

$\llbracket s \rrbracket^\sharp(a)=\min \{a'\mid a'\sqsubset a, a'\models s\}$

\pscmt{define $a'\models s$}

We define a specialised variant of the transformer to compute deductions w.r.t.\ a given subdomain $L\subseteq A$.

$\llbracket s \rrbracket^\sharp(a,L)=\min \{a'\mid a'\sqsubset a, a'\in L, a'\models s\}$

We have the property $\llbracket s \rrbracket^\sharp(a)\sqsubseteq a\meet\llbracket s \rrbracket^\sharp(a,L)$.

For example,
$a=(0\leq y \leq 1 \wedge 5\leq z)$
$\llbracket x=y+z\rrbracket^\sharp(a,\{x\})=(x\geq 6)$, whereas
$\llbracket x=y+z\rrbracket^\sharp(a,\{y\})=\top$.

%$a=(x-y \leq 1, y-x \leq 1)$
%$\llbracket x=y+z\rrbracket^\sharp($

Moreover, we want to know what the reasons for a specific deduction are.
$ded(s,a,L)=\{R\rightarrow d\mid R=reason(s,a,L,d), d \in decomp(\llbracket s \rrbracket^\sharp(a,L))\}$
where 
$reason(s,a,L,d)=\min \{R'\mid R'\subseteq decomp(a), \llbracket s\rrbracket^\sharp(R,L)=d\}$.

\pscmt{TODO from here}

@@

% For a program with $N$ variables, let $L$ be the total number of 
% meet irreducibles returned by a domain $D$.  For $D$ = {\em ItvDom}, the 
% maximum value of $L$ is $2*N$, whereas the maximum value of $L$ is 
% $2*(N^2)$ for $D$ = {\em OctDom}. Note that an octagon is the conjunction 
% of all octagonal inequalities in the set $L$.
%
%========================
%\input{literals-clauses}
%========================
